Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-04-12 paper/ms.tex
new sections in the paper, more structured

>>>>

\section{Discussion}

The raw results of our experiments yield a prefered range for
halo masses hosting LAES is in the range $10^{10}\hMsun<M_{\rm
  min}<10^{11.5}\hMsun$, without any limitation in the  maximum mass,
plus an average occupation fraction as a function of the minimum mass
$f_{occ}\approx 0.1 (M_{\rm min}/10^{10})^{XX}$. This exercise was
useful to discard models that were nevertheless disfavored from the
very beginning based on the results of the mass functions (see Figure 1.).

In this discussion section we consider different ways to impose tighter
constraints by making use of the results we have derived so far and
using additional statistical and astrophysical constraints. We will
consider three different constraints. The first is based on
models with high fractions of mock surveys that are consistent with
observations. The second uses observational results on the occupation
fraction. The third exploits the observational information in the Angular
Correlation Function.

\subsection{Models with highest success rates}
\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a mininium number of mock survey
  realizations that are consistent with observations.
  \label{figure:high_success_rate}.}  
\end{figure*}

For each model there are 15 different realizations of mock surveys. In
the loose constraints of the previous sections, each model has at
least one (1) realization of mock survey with $P>0.05$. In Figure XX
we show the number of models that have at least $n$ realizations with
$P>0.05$ for the {\texttt match} and {\texttt random} methods.

This Figure shows that there are around $550$ to $600$ different
models that have at leaset one mock survey realization consistent with
observations. At the other extreme, there are $80$ to $100$ models
with all the 15 realizations with $P>0.05$. Here we focuse on the
latter models.
